--- 
title: "R cookbook from Xiaotao Shen"
author: '<br><br>Dr. Xiaotao Shen <br> Postdoctoral at <a href="http://snyderlab.stanford.edu/" target="_blank">Snyder lab</a> <br> Stanford University School of Medicine <br> <a href="http://shenxt.info" target="_blank"> <i class="fa fa-home fa-fw"></i>&nbsp; shenxt.info</a><br> <a href="mailto:shenxt@stanford.edu" target="_blank"><i class="fa fa-paper-plane fa-fw"></i>&nbsp; shenxt@stanford.edu</a><br>'
date: "Begin at 2020-03-01 and Update at `r Sys.Date()`"
site: bookdown::bookdown_site
output:
  bookdown::html_book:
    includes: 
      after_body: disqus.html
    highlight: tango
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yesss
description: "记录所有跟R语言有关的内容"
github-repo: 'jaspershen/r_cookbook'
---

# Welcome {-}

这本书用来系统记录在学习过程中的遇到的问题,学到的知识.

You can contact me via the social websites below:

<a href="https://www.shenxt.info/" target='_blank'><i class="fa fa-home"> Personal website</i></a> 

<a href="https://github.com/jaspershen" target='_blank'><i class="fa fa-github"> Github</i></a> 

<a href="https://www.shenxt.info/files/wechat_QR.jpg" target='_blank'><i class="fa fa-weixin"> Wechat</i></a> 

<a href="https://www.shenxt.info/files/qq_QR.jpg" target='_blank'><i class="fa fa-qq"> QQ</i></a> 

<a href="shenxt@stanford.edu" target='_blank'><i class="fa fa-envelope">  shenxt at stanford.edu</i></a> 

<a href="https://www.linkedin.com/in/shenxt/" target='_blank'><i class="fa fa-linkedin"> Linkedin</i></a>

```{r, eval = TRUE, echo = FALSE}
library(leaflet)
leaflet() %>% addTiles() %>%
  setView(-122.176758, 37.432748, zoom = 17) %>%
  addPopups(
    -122.176758, 37.432748,
    'My office is <b>M339, Alway Building, Cooper Lane, Palo Alto, CA 94304'
  )
```



```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

---

<div id="disqus_thread"></div>
<script>

/**
*  RECOMMENDED CONFIGURATION VARIABLES: EDIT AND UNCOMMENT THE SECTION BELOW TO INSERT DYNAMIC VALUES FROM YOUR PLATFORM OR CMS.
*  LEARN WHY DEFINING THESE VARIABLES IS IMPORTANT: https://disqus.com/admin/universalcode/#configuration-variables*/
/*
var disqus_config = function () {
this.page.url = PAGE_URL;  // Replace PAGE_URL with your page's canonical URL variable
this.page.identifier = PAGE_IDENTIFIER; // Replace PAGE_IDENTIFIER with your page's unique identifier variable
};
*/
(function() { // DON'T EDIT BELOW THIS LINE
var d = document, s = d.createElement('script');
s.src = 'https://r-cookbook-shen.disqus.com/embed.js';
s.setAttribute('data-timestamp', +new Date());
(d.head || d.body).appendChild(s);
})();
</script>
<noscript>Please enable JavaScript to view the <a href="https://disqus.com/?ref_noscript">comments powered by Disqus.</a></noscript>
                            